\Title

### 2016-03-21 manuscript/manuscript.tex
Figure with residuals and seismic diffs
For the South America model. Plot the tectonic provinces without names.

\documentclass[extra,mreferee]{gji}
%\documentclass[extra]{gji}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{url}
\usepackage[utf8]{inputenc}
% To make two column figures appear in the correct order
\usepackage{fixltx2e}
% To make annotations on the sides
\usepackage{todonotes}

@@

>>>>

%\documentclass[extra,mreferee]{gji}
\documentclass[extra]{gji}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{url}
\usepackage[utf8]{inputenc}
% To make two column figures appear in the correct order
\usepackage{fixltx2e}
% To make annotations on the sides
\usepackage{todonotes}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/south-america-residuals}
    \caption{
        Inversion results for the South American Moho.
        (a) Inversion residuals (observed data in Fig.~\ref{fig:sam-data}a
        minus the data predicted by the estimate (a)).
        (b) Differences between the seismological depths of
        \citet{assumpcao2013a} and our gravity-derived Moho depth estimate
        (Fig.~\ref{fig:sam-moho}).
        The inset in b shows a histogram of the differences along with their
        calculated mean and standard deviation (std).
    }
    \label{fig:sam-residuals}
\end{figure*}
